\section{State-of-the-art and related work}

\begin{frame}

    \frametitle{Existing text-based game agents}
    \begin{description}
        \item[BYUAgent]

            Extracts nouns from game text and combines them with
            pre-generated verb list, with the help of word embeddings.
            Stores verb/noun combinations that produce a result. Winner
            of IEEE CIG 2016 Text-based adventure AI competition.
        \item[Golovin]

            Operates in one of 5 command generator modes, based on
            current game environment. Uses word embeddings trained
            on text-based game walkthroughs, tutorials and narrative
            fiction.
        \item[NAIL]

            Independent modules compete for control of the agent based
            on \emph{eagerness}. Uses a knowledge graph to track world
            state. Relies on heavily tuned command sets common to
            text-based games. Winner of IEEE CIG 2018 Text-based AI
            competition.
    \end{description}
    (\cite{atkinson_text-based_2019}, \cite{ricks_byu-agent-2016_2019},
    \cite{hausknecht_nail_2019})

\end{frame}

\begin{frame}
    \frametitle{AI frameworks for text-based games}
    \begin{description}
        \item[Jericho]

            A python-based library for using learning agents with
            text-based games.
            \parencite{hausknecht_interactive_2020}
        \item[TextWorld]
            
            A python-based library for procedurally generating
            text-based games.
            \parencite{cote_textworld_2019}
    \end{description}
\end{frame}
